Verifying Demonstrations

### 2019-02-26 paper/protocol.tex
fixes space, acf errors

We now present \CROCUS, a protocol for privately verifiable crowd
counts. A prerequisite for using \CROCUS is a one-to-one mapping of a person's
sybil-proof identity and a cryptographic key
%, more specifically, an anonymous 
%identity credential that provides unlinkability between contexts but 
%linkability for reuse within the same context
%\sonja{this is actually achieved by our use of prfs for pid and wid,
%not inherent in the credential}
% \footnote{%
%   Given any \ac{CA} that prevents Sybil 
%   attacks~\cite{SybilAttack}, systems such as~\cite{clonewars} could
%   be used to make sure that for each identity one-and-only-one
%   cryptographic key is issued.
%   In terms of~\cite{clonewars}, this can be seen as an unclonable subscription 
%   to one's identity.
% }
. Since we assume these properties, we
present only the result of the process of getting anonymous
credentials from a \ac{CA}, in \cref{ProtocolSetup}.

@@

The protester sends \(\pid\) to the witness.
Then they run the protocol \[
  \Proto{\ACproveSig[\spk, k, r, \sigma]}{\ACverifySig[\spk, \ssk]}
\] (see \cref{ACacAlg}).
Note that the proof of knowledge (\ac{PK}) in \cref{ACacAlg} must be
run as a proof of proximity (\iac{PPK}), which we do by distance bounding.
If the protocol succeeds, the witness will compute \(\wid \gets 
  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.

>>>>

We now present \CROCUS, a protocol for privately verifiable crowd
counts. A prerequisite for using \CROCUS is a one-to-one mapping of a person's
sybil-proof identity and a cryptographic key%
%, more specifically, an anonymous 
%identity credential that provides unlinkability between contexts but 
%linkability for reuse within the same context
%\sonja{this is actually achieved by our use of prfs for pid and wid,
%not inherent in the credential}
% \footnote{%
%   Given any \ac{CA} that prevents Sybil 
%   attacks~\cite{SybilAttack}, systems such as~\cite{clonewars} could
%   be used to make sure that for each identity one-and-only-one
%   cryptographic key is issued.
%   In terms of~\cite{clonewars}, this can be seen as an unclonable subscription 
%   to one's identity.
% }
. Since we assume these properties, we
present only the result of the process of getting anonymous
credentials from a \ac{CA}, in \cref{ProtocolSetup}.

@@

The protester sends \(\pid\) to the witness.
Then they run the protocol \[
  \Proto{\ACproveSig[\spk, k, r, \sigma]}{\ACverifySig[\spk, \ssk]}
\] (see \cref{ACacAlg}).
Note that the \acf{PK} in \cref{ACacAlg} must be
run as a \iacf{PPK}, which we do by distance bounding.
If the protocol succeeds, the witness will compute \(\wid \gets 
  \ACprf[_{\sk_W}][\pid]\) and send \((\wid, t_s', l)\) to the protester.
